Interactive web based flood modeling at country wide scale and planter size resolution.

### 2014-03-21 article.tex
writing

%
These advances in the numerical model allow the model to act as a component in the interactive web-based model environment that will be described in the next section.

@@

To enable social and interactive modeling through a map environment the most logical choice was to use a web based environment. Over the last years this choice has become easier through the large list of advancements for browser based applications.  An overview of the architecture is given in \autoref{fig:arch}. Notice how the architectural follows the general Model View Controller pattern \citep{GOF2004}. On a high level the architecture follows is classic. In this section we will describe the lower level, yet important,  technical innovations that made the application of this architecture successful.

@@

\begin{acronym}[AAAAA]
\acro{H2O}[$\mathrm{H_2O}$]{water}
\acro{BMI}{Basic Model Interface}
\acro{API}{Application Programming Interface}
\acro{GUI}{Graphical User Interface}
\acro{DEM}{Digital Elevation Model}
\acro{HTTP}{Hyper Text Transfer Protocol}
\acro{IaaS}{Infrastructure as a Service}
\end{acronym}

>>>>

These advances in the numerical model allow the model to act as a component in the interactive web-based model environment that will be described in the next section.

@@

To enable social and interactive modeling through a map environment the most logical choice was to use a web based environment. Over the last years this choice has become easier. The large list of browser enhancements (for example inline \ac{SVG}, canvas, plugin free video \citep{Berjon2014} and \ac{CSS} animations \citep{Jackson2013}) allow for rich visualizations. An overview of the architecture is given in \autoref{fig:arch}. Notice how the architectural follows the general Model View Controller pattern \citep{Gamma1994}. On a high level the architecture follows is classic. In this section we will describe the lower level, yet important,  technical innovations that made the application of this architecture successful.

@@

\begin{acronym}[AAAAA]
\acro{CSS}{Cascading Style Sheets}
\acro{SVG}{Scalable Vector Graphics}
\acro{H2O}[$\mathrm{H_2O}$]{water}
\acro{BMI}{Basic Model Interface}
\acro{API}{Application Programming Interface}
\acro{GUI}{Graphical User Interface}
\acro{DEM}{Digital Elevation Model}
\acro{HTTP}{Hyper Text Transfer Protocol}
\acro{IaaS}{Infrastructure as a Service}
\end{acronym}
